Predicting sales of newly published books

### 2015-08-12 paper.tex
comentarios

Then, after analizyng the original dataset using the SOM to select the best variables to be considered, and taking into account the knowledge of the company experienced manager, 13 inputs were considered. 
Figure \ref{fig:som43} shows the initial analisys of dataset using the total of 43 descriptive inputs per book.
Table \ref{tabla:params13} shows the set of variables describing a book after the second analisys.
	% esta gráfica no aporta nada, ni la siguiente tampoco. No se puede
	% colocar en un trabajo en revista  cómo ha ido el entrenamiento, sino
	% datos serios de análisis estadístico de las variables. 
	% [Pedro] ¿a qué gráficas te refieres? ¿a las tablas de las variables?
% NO, a fig:som43, creo, porque ha desaparecido. - JJ
\begin{figure}[!h] 
\begin{center}
\begin{tabular}{c}
  \epsfig{file=som43vars.eps,width=11cm} \\
  \epsfig{file=som43umatrix.eps,width=5cm}
\end{tabular}
\caption{\small{Initial data analysis, using 43 descriptive variables per bok, using SOM.}}
	% Cojollos, ¿qué trabajo os cuesta poner esto en inglés directamente? - JJ
	% [Pedro] sí, si estoy de acuerdo... hay días que me "sale" el texto en inglés,
	% pero hay días que soltar la parrafada en español me resulta más fácil    :/
        % Sería más bien exploratory data analysis o data visualization. Un gráfico no es un análisis. Y pon las cosas cortas en inglés, hombre - JJ
\label{fig:som43}
\end{center}
\end{figure}

\begin{table}[!h]
\caption{Variables that describe every book, 13 in total, after the
  second analysis carried out using the SOM along with the company
  experienced manager % él no hizo el análisis. No cuela con ``along
                      % with'' - JJ
to select the best variables to be considered to
  solve the sales forecasting problem.} 
\label{tabla:params13}
\begin{center}
\begin{tabular}{|c|}
\hline

>>>>

Then, after analizyng the original dataset using the SOM to select the best variables to be considered, and taking into account the knowledge of the company experienced manager, 13 inputs were considered. 
Figure \ref{fig:som43} shows the initial analisys of dataset using the total of 43 descriptive inputs per book.
Table \ref{tabla:params13} shows the set of variables describing a book after the second analisys.
	% esta gráfica no aporta nada, ni la siguiente tampoco. No se puede
	% colocar en un trabajo en revista  cómo ha ido el entrenamiento, sino
	% datos serios de análisis estadístico de las variables. 
	% [Pedro] ¿a qué gráficas te refieres? ¿a las tablas de las variables?
% NO, a fig:som43, creo, porque ha desaparecido. - JJ
\begin{figure}[!h] 
\begin{center}
\begin{tabular}{c}
  \epsfig{file=som43vars.eps,width=11cm} \\
  \epsfig{file=som43umatrix.eps,width=5cm}
\end{tabular}
\caption{\small{Initial data analysis, using 43 descriptive variables per book, using SOM.}}
	% Cojollos, ¿qué trabajo os cuesta poner esto en inglés directamente? - JJ
	% [Pedro] sí, si estoy de acuerdo... hay días que me "sale" el texto en inglés,
	% pero hay días que soltar la parrafada en español me resulta más fácil    :/
        % Sería más bien exploratory data analysis o data visualization. Un gráfico no es un análisis. Y pon las cosas cortas en inglés, hombre - JJ
\label{fig:som43}
\end{center}
\end{figure}

\begin{table}[!h]
\caption{Variables that describe every book, 13 in total, after the
  second analysis carried out using the SOM along with the company
  experienced manager % él no hizo el análisis. No cuela con ``along with'' - JJ
to select the best variables to be considered to
  solve the sales forecasting problem.} 
\label{tabla:params13}
\begin{center}
\begin{tabular}{|c|}
\hline
